---
title: "PMW Final"
author: "Anna Ben-Hamou, Philippe Naveau and Maud Thomas"
date: '2022-10-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(22032023)
```

```{r packages}
libs <- c('ExtDist', 'Rfast', 'ggplot2', 'splitTools', 'extRemes', 'dplyr', 'latex2exp')
sapply(libs,require,character.only = T, quietly = TRUE, warn.conflicts = FALSE)
```

## Preambule

Recall the notations

$\theta_{k:m} = \mathbb{E}[X_{(k:m)}]$ and $\hat \theta_{k:m}$ the Median-of-means estimator of $\theta_{k:m}$

$\xi$ = tail index

$$
\xi = \log_2 \left(\frac{\theta_{4:4} - \theta_{2:2} }{\theta_{2:2} - \theta_{1:1} }\right).
$$

and can thus be estimated by

$$
\hat \xi_n = \log_2 \left(\frac{\hat\theta_{4:4} - \hat\theta_{2:2} }{\hat\theta_{2:2} - \hat\theta_{1:1} }\right)
$$

# Functions

## Benchmarks

### Expectation of the k-th order statistic of a sample size m

We compute $\theta_{k:m} = \mathbb{E}[X_{(k:m)}]$ using Monte Carlo simulations as a benchmark.

```{r Theta}
Theta <- function(data, m, k){
  n_data <- length(data)
  nb.simus <- floor(n_data/m)
  df.data <- matrix(data = data, nrow = nb.simus, ncol = m, byrow = F)
  theta_vec <- apply(X = df.data, MARGIN = 1, FUN = function(x){nth(x=sort(x), n = k)})
  return(mean(theta_vec))
}
```

### True value of tail index $\xi$ (not useful if we only consider GEV)

```{r xi}
xi <- function(data){
  theta4 <- Theta(data = data, m = 4, k = 4)
  theta2 <- Theta(data = data, m = 2, k = 2)
  theta1 <- Theta(data = data, m = 1, k = 1)
  return(log((theta4-theta2)/(theta2-theta1), base = 2))
}
```

## Estimators

### Classical estimator $\hat \theta_{k:m}$ of $\theta_{k:m}$

```{r CombLinear}
CombLinear <- function(data, m, k){
  n <- length(data)
  a <- apply(X = matrix(data = 1:n, nrow = 1, byrow = T), MARGIN = 1, FUN = function(x){choose(x-1,k-1)*choose(n-x, m-k)/choose(n,m)})
  return(sum(a*sort(data)))
}
```

### Median-of-means estimator $\hat \theta_{k:m}$ of $\theta_{k:m}$

```{r thetaMM}
thetaMM <- function(data,  m, k, delta){
  n <- length(data)
  stopifnot((exp(-n/m) <= delta) & (delta<1))
  K <- ceiling(log(1/delta)) # nb of blocks
  stopifnot(K <= n/m)
  data_block <- split(data,cut(seq_along(data),
          K,
          labels = FALSE))
 return(median(x = unlist(lapply(X = data_block, FUN = CombLinear, m = m, k = k))))
}
```

### Median of means estimator $\hat \xi_{MM}$ of $\xi$

```{r xiMM}
xiMM <- function(data, delta){
  theta4 <- thetaMM(data = data, m = 4, k = 4, delta = delta)
  theta2 <- thetaMM(data = data, m = 2, k = 2, delta = delta)
  theta1 <- thetaMM(data = data, m = 1, k = 1, delta = delta)
  return(log((theta4-theta2)/(theta2-theta1), base = 2))
}
```

### Classical estimator $\hat \xi_{CL}$ of $\xi$

```{r xiCL}
xiCL <- function(data){
  theta4 <- CombLinear(data = data, m = 4, k = 4)
  theta2 <- CombLinear(data = data, m = 2, k = 2)
  theta1 <- CombLinear(data = data, m = 1, k = 1)
  return(log((theta4-theta2)/(theta2-theta1), base = 2))
}
```

### Simulations of GEV + outliers for $\xi <0$

```{r GEVoutliersNeg}
GEVoutliersNeg <- function(nb_n, nb_o, xi_n,rho){
GEVnormal <- revd(n = nb_n, loc = 0, 1, shape = xi_n)

 outliers <- runif(n = nb_o, min = 1, max = rho)-1/xi_n
data <- c(GEVnormal, outliers)
  return(data)
}
```

### Simulations of GEV + outliers for $\xi >=0$

```{r GEVoutliersPos}
GEVoutliersPos <- function(nb_n, nb_o, xi_n,a){
GEVnormal <- revd(n = nb_n, loc = 0, scale= 1, shape = xi_n)

 outliers <- qevd(p = 1-10^(-a), loc = mu, scale = sigma, shape = xi_n) + rnorm(n = nb_o,mean = 0, sd =1)
data <- c(GEVnormal, outliers)
  return(data)
}
```


## for theta_{1:2}

```{r}
n <- 200

k <- 1
m <- 2

mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA.df <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta12 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta12 <- plot_theta12 + geom_hline(data = THETA.df, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta12 <- plot_theta12 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta12
```

## for theta_{2:2}

```{r}
n <- 200

k <- 2
m <- 2

mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA.df <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta22 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta22 <- plot_theta22 + geom_hline(data = THETA.df, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta22 <- plot_theta22 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta22
```


## for theta_{1:3}

```{r}
n <- 200

k <- 1
m <- 3

mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA.df <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta13 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta13 <- plot_theta13 + geom_hline(data = THETA.df, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta13 <- plot_theta13 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta13
```

## for theta_{2:3}

```{r}
n <- 200

k <- 2
m <- 3

mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA.df <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta23 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta23 <- plot_theta23 + geom_hline(data = THETA.df, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta23 <- plot_theta23 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta23
```

## for theta_{3:3}

```{r}
n <- 200

k <- 3
m <- 3

mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA.df <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta33 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta33 <- plot_theta33 + geom_hline(data = THETA.df, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta33 <- plot_theta33 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta33
```


## for theta_{1:4}

```{r}
n <- 200

k <- 1
m <- 4

mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA.df <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta14 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta14 <- plot_theta14 + geom_hline(data = THETA.df, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta14 <- plot_theta14 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta14
```

## for theta_{2:4}

```{r}
n <- 200

k <- 2
m <- 4

mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA.df <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta24 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta24 <- plot_theta24 + geom_hline(data = THETA.df, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta24 <- plot_theta24 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta24
```


## for theta_{3:4}

```{r}

k <- 3
m <- 4


n <- 200


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4

xi_neg <- -0.4

n1 <- 1e6
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta34 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta34 <- plot_theta34 + geom_hline(data = THETA, aes(yintercept = Z), linetype = 2, col = "blue")+ theme(legend.position = "none")
plot_theta34 <- plot_theta34 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)'))  + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta34
```


## for theta_{4:4}

```{r}

k <- 4
m <- 4



n <- 200


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4
n1 <- 1e6
xi_neg <- -0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_neg, type = "GEV")
theta_neg <- Theta(data = simul, k = k, m =m)

df.est.thetaNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaNeg[df.est.thetaNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}


df.est.thetaNeg$nbOutliers <- as.factor(df.est.thetaNeg$nbOutliers)
df.est.thetaNeg$Xi <- as.factor(rep(-0.4, length(df.est.thetaNeg$Est)))

xi_0 <- 0
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_0, type = "GEV")
theta_0 <- Theta(data = simul, k = k, m =m)

df.est.theta0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.theta0[df.est.theta0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.theta0$nbOutliers <- as.factor(df.est.theta0$nbOutliers)
df.est.theta0$Xi <- as.factor(rep(0, length(df.est.theta0$Est)))
df.est.theta <- rbind(df.est.thetaNeg, df.est.theta0)

xi_pos <- 0.4
simul <- revd(n = n1,loc = mu, scale = sigma, shape = xi_pos, type = "GEV")
theta_pos <- Theta(data = simul, k = k, m =m)

df.est.thetaPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = CombLinear, k=k, m=m)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = thetaMM, k=k, m=m, delta = delta)
df.est.thetaPos[df.est.thetaPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
}

df.est.thetaPos$nbOutliers <- as.factor(df.est.thetaPos$nbOutliers)
df.est.thetaPos$Xi <- as.factor(rep(0.4, length(df.est.thetaPos$Est)))

df.est.theta <- rbind(df.est.theta, df.est.thetaPos)
```

```{r}
THETA <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(theta_neg, theta_0, theta_pos))

plot_theta44 <- ggplot(data = df.est.theta, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_theta44  <- plot_theta44  + geom_hline(data = THETA, aes(yintercept = Z), linetype = 2, col = "blue") + theme(legend.position = "none")
plot_theta44 <- plot_theta44 + ylab("Estimates") + xlab(TeX(r'($n_{O}$)')) + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_theta44 
```



### xi + return level

```{r}
n <- 200
mu <- 0
sigma <- 1


nb_o <- c(0,5, 15,20)
delta  <- 1e-2
nb.rep <- 1e3
rho <- 20
a <- 4
level <- 0.95

xi_neg <- -0.4
q_neg <- qevd(p = level, loc = 0, scale = 1, shape = xi_neg)

df.est.xiNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

df.est.RLNeg <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), RL=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))


for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersNeg(nb_n = (n-i), nb_o = i, xi_n = xi_neg, rho = rho))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = xiCL)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = xiMM,  delta = delta)
df.rlcl <- sapply(X=df.cl,  FUN = function(x){qevd(p = level,loc = 0, scale = 1, shape = x)})
df.rlmm <- sapply(X=df.mm,  FUN = function(x){qevd(p = level,loc = 0, scale = 1, shape = x)})
df.est.xiNeg[df.est.xiNeg$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
df.est.RLNeg[df.est.RLNeg$nbOutliers == i, ]$RL <- c(df.rlcl, df.rlmm)
}

df.est.xiNeg$nbOutliers <- as.factor(df.est.xiNeg$nbOutliers)
df.est.xiNeg$Xi <- as.factor(rep(-0.4, length(df.est.xiNeg$Est)))

df.est.RLNeg$nbOutliers <- as.factor(df.est.RLNeg$nbOutliers)
df.est.RLNeg$Xi <-  df.est.xiNeg$Xi

xi_0 <- 0
q_0 <- qevd(p = level, loc = 0, scale = 1, shape = xi_0)

df.est.xi0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

df.est.RL0 <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), RL=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))


for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
  x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_0, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = xiCL)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = xiMM,  delta = delta)
df.rlcl <- sapply(X=df.cl,  FUN = function(x){qevd(p = level,loc = 0, scale = 1, shape = x)})
df.rlmm <- sapply(X=df.mm,  FUN = function(x){qevd(p = level,loc = 0, scale = 1, shape = x)})
df.est.xi0[df.est.xi0$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
df.est.RL0[df.est.RL0$nbOutliers == i, ]$RL <- c(df.rlcl, df.rlmm)
}

df.est.xi0$nbOutliers <- as.factor(df.est.xi0$nbOutliers)
df.est.xi0$Xi <- as.factor(rep(0, length(df.est.xi0$Est)))

df.est.RL0$nbOutliers <- as.factor(df.est.RL0$nbOutliers)
df.est.RL0$Xi <-  df.est.xi0$Xi


df.est.xi <- rbind(df.est.xiNeg, df.est.xi0)
df.est.rl <- rbind(df.est.RLNeg, df.est.RL0)


xi_pos <- 0.4
q_pos <- qevd(p = level, loc = 0, scale = 1, shape = xi_pos)

df.est.xiPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), Est=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))

df.est.RLPos <- data.frame(nbOutliers=rep(x = nb_o, each = 2*nb.rep), RL=rep(0, 2*length(nb_o)*nb.rep), Group = rep(c(rep("LC", nb.rep), rep('MM', nb.rep)), length(nb_o)))


for (i in nb_o){
  x <- c()
  for (j in 1:nb.rep){
   x <- c(x,GEVoutliersPos(nb_n = (n-i), nb_o = i, xi_n = xi_pos, a=a))
  }
df.x <- matrix(data = x, nrow = n, ncol = nb.rep, byrow = F)
df.cl <- apply(X = df.x, MARGIN = 2, FUN = xiCL)
df.mm <- apply(X = df.x, MARGIN = 2, FUN = xiMM,  delta = delta)
df.rlcl <- sapply(X=df.cl,  FUN = function(x){qevd(p = level,loc = 0, scale = 1, shape = x)})
df.rlmm <- sapply(X=df.mm,  FUN = function(x){qevd(p = level,loc = 0, scale = 1, shape = x)})
df.est.xiPos[df.est.xiPos$nbOutliers == i, ]$Est <- c(df.cl, df.mm)
df.est.RLPos[df.est.RLPos$nbOutliers == i, ]$RL <- c(df.rlcl, df.rlmm)
}

df.est.xiPos$nbOutliers <- as.factor(df.est.xiPos$nbOutliers)
df.est.xiPos$Xi <- as.factor(rep(0.4, length(df.est.xiPos$Est)))

df.est.RLPos$nbOutliers <- as.factor(df.est.RLPos$nbOutliers)
df.est.RLPos$Xi <-  df.est.xiPos$Xi




df.est.xi <- rbind(df.est.xi, df.est.xiPos)
df.est.rl <- rbind(df.est.rl, df.est.RLPos)

```

```{r}
XI <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(xi_neg, xi_0, xi_pos))

plot_xi <- ggplot(data = df.est.xi, aes(x = nbOutliers, y = Est, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_xi <- plot_xi + geom_hline(data = XI, aes(yintercept = Z), linetype = 2, col = "blue") + theme(legend.position = "none")
plot_xi <- plot_xi + ylab("Estimates") + xlab(TeX(r'($n_{O}$)')) + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_xi
```

```{r}
RL <- data.frame(Xi = c("-0.4", "0", "0.4"), Z = c(q_neg, q_0, q_pos))

plot_rl <- ggplot(data = df.est.rl, aes(x = nbOutliers, y = RL, fill = Group)) + geom_boxplot()  + coord_flip() + facet_grid(rows = vars(Group),cols = vars(Xi))
plot_rl <- plot_rl + geom_hline(data = RL, aes(yintercept = Z), linetype = 2, col = "blue") + theme(legend.position = "none")
plot_rl <- plot_rl + ylab("Estimates") + xlab(TeX(r'($n_{O}$)')) + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14))
plot_rl
```
